---
title: "EconData"
author: Created by Bradley Setzler, University of Chicago
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This is a directory for managing publicly-available economics data. It contains two components:

- [EconData](https://github.com/setzler/EconData/tree/master/EconData): R package to automatically download and prepare various publicly-available economic data sets from source.
- [DataRepo](https://github.com/setzler/EconData/tree/master/DataRepo) A repository of prepared data sets that were created by the EconData package.

To use the R package, run the following:

```{r echo=T, eval=F}
devtools::install_github("setzler/EconData/EconData")
```
```{r echo=T, eval=T, warning=FALSE}
library(EconData)
```

Data sets currently available include:

- [State corporate tax rates](https://github.com/setzler/EconData/tree/master/DataRepo/StateCorpTax/), covering all states during 2000-2020.
- [Census CBP](https://github.com/setzler/EconData/tree/master/DataRepo/CensusCBP/) employment, earnings, and establishments at various levels of aggregation, 2001-2017.
- [Miscellaneous](https://github.com/setzler/EconData/tree/master/DataRepo/Miscellaneous/) cross-walks, distances, and industry classifications.

