---
title: "Miscellaneous Public Data Sets"
author: Created by Bradley Setzler, University of Chicago
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=F, eval=T, warning=FALSE, comment=FALSE, warning=FALSE}
library(data.table)
library(ggplot2)
library(scales)
library(knitr)
```



[Prepared Miscellaneous data sets are located here.](https://github.com/setzler/EconData/tree/master/DataRepo/Miscellaneous/)


Included files and functions include:

- `state_fips_crosswalk.csv`: Cross-walk from state FIPS to name of the state. When `getCZ()` function is run, it downloads and cleans the data from the USDA.

- `cz_crosswalk_2000.csv`: Cross-walk from county FIPS to 2000 commuting zone. When `getStateFips()` function is run, it downloads and cleans the data from the Census.

- `MianSufi2014_tradables.csv`: Tradable vs non-tradable industry classification from Mian and Sufi (2014, Econometrica). When `getTradables()` is run, it downloads and cleans the data from Sufi's website.

- `distances/county_distance_100miles.csv`, `distances/CZ_distance_100miles.csv`, and `distances/state_distance_100miles.csv`: Using county-to-county distances of up to 100 miles, it forms the minimum between counties, commuting zones, and states, respectively. Any pairs not included are over 100 miles apart. When `getDistances()` is run, it downloads and cleans the distances the NBER data repository.


